Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-04-20 paper.tex
Some spelling corrections.

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such
software, based on the CDK and Open Babel, respectively. Bioclipse is
an award-winning `molecular workbench' for life sciences with a dynamic plugin architectur, and which wraps cheminformatics functionality behind user-friendly interfaces and graphical editors. All functionality in Bioclipse is completely scriptable using an integrated high-level language called Bioclipse Scripting Language (BSL), which can be used for invoking functionality or to automate complex tasks~\cite{Bioclipse2}.

>>>>

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such
software, based on the CDK and Open Babel, respectively. Bioclipse is
an award-winning molecular workbench for life sciences with a dynamic plugin architecture, and which wraps cheminformatics functionality behind user-friendly interfaces and graphical editors. All functionality in Bioclipse is completely scriptable using an integrated high-level language called Bioclipse Scripting Language (BSL), which can be used for scripted research or to automate complex tasks~\cite{Bioclipse2}.
